---
title: "3.7.1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}

library(fpp3)

```

# 3.7 Exercises


## 1. Consider the GDP information in global_economy. Plot the GDP per capita for each country over time. Which country has the highest GDP per capita? How has this changed over time?


### Plot the GDP per capita for each country over time.


#### Take a look at the dataset

```{r}

data("global_economy")

head(global_economy)

```

#### Let's look at the number of countries in the dataset

```{r}

unique(global_economy$Country)
```
#### Select a subset of countries to plot

```{r}

global_economy %>%
  filter(Country %in% c("Australia", "Canada", "France", "Germany", "Luxembourg", "Netherlands", "New Zealand", "OECD members", "Singapore", "Spain", "Switzerland", "United Kingdom", "United States")) %>%
  autoplot() +
  labs(title= "GDP total", y = "$US")

```

```{r}

global_economy %>%
  filter(Country %in% c("Australia", "Canada", "France", "Germany", "Luxembourg", "Netherlands", "New Zealand", "Singapore", "Spain", "Switzerland", "United Kingdom")) %>%
  autoplot() +
  labs(title= "GDP total", y = "$US")

```

```{r}

global_economy %>%
  filter(Country %in% c("Australia", "Canada", "France", "Germany", "Luxembourg", "Netherlands", "New Zealand", "Singapore", "Spain", "Switzerland", "United Kingdom", "United States")) %>%
  autoplot(GDP/Population)+
  labs(title= "GDP per capita", y = "$US")

```

```{r}

global_economy %>%
  filter(Country %in% c("Australia", "Canada", "Luxembourg", "New Zealand", "United Kingdom", "United States")) %>%
  autoplot(GDP/Population)+
  labs(title= "GDP per capita", y = "$US")

```
### Which country has the highest GDP per capita?

```{r}
global_economy %>%
  mutate(GDP_per_capita = (GDP/Population)) %>%
  filter(GDP_per_capita == max(GDP_per_capita, na.rm = TRUE))
```
### How has this changed over time?

#### Changes in Monaco's GDP over time

```{r}
global_economy %>%
  filter(Country %in% c("Monaco")) %>%
  autoplot(GDP/Population)+
  labs(title= "GDP per capita", y = "$US")
```

#### Country with the highest GDP every year

```{r}

global_economy %>%
  mutate(GDP_per_capita = (GDP/Population)) %>%
  filter(!Country %in% c("World", "High income", "OECD members", "Post-demographic dividend", "Europe & Central Asia", "European Union", "East Asia & Pacific", "IDA & IBRD total", "Low & middle income", "IBRD only", "Middle income", "North America", "Euro area")) %>%
  as_tibble() %>%
  group_by(Year) %>%
  filter(GDP_per_capita == max(GDP_per_capita, na.rm = TRUE)) %>%
  ungroup() %>%
  select(Year, Country, GDP_per_capita) %>%
  arrange(desc(Year))

```
#### Monaco vs Liechtenstein vs Luxembourg

```{r}
global_economy %>%
  filter(Country %in% c("Monaco", "Liechtenstein", "Luxembourg")) %>%
  autoplot(GDP/Population)+
  labs(title= "GDP per capita", y = "$US")
```
